---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "75%"
)
```

# Register and consonance

<!-- badges: start -->
<!-- badges: end -->

This repository contains data and analysis concerning study titled "Register Impacts Perceptual Consonance through Roughness and Sharpness" by XXXX XXXXX XXXXXX XXXXX.



## Background

```{r register,message=FALSE, warning=FALSE,echo=FALSE,fig.width=9,fig.height=5,fig.cap='Panel A: 7 stimulus registers overlaid on an idealised distribution of orchestral instrument ranges (from Huron, 2001, p.8). Panel B: Calculated roughness and sharpness values for different chords across the stimulus registers.'}
source('predictions.R')
print(G)
```

## Stimuli

```{r stim,echo=FALSE, cache=TRUE}
d <- read.csv('tetrads_4_rich.csv',header = TRUE)
knitr::kable(d,caption = 'Stimulus details.',format = 'simple')
```


## Load and preprocess the data

```{r initial,message=FALSE,warning=FALSE,echo=FALSE,cache=TRUE}

library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(papaja)
library(psych)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)

source('load_and_preprocess_data.R')
```

### Summarise consonance ratings

```{r summary,echo=FALSE}
options(dplyr.summarise.inform = FALSE)
source('summarise_means.R')
```

### Linear mixed model

```{r LMM, message=FALSE, warning=FALSE,echo=FALSE,cache=TRUE,results='asis'}
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(papaja)
library(psych)
source('LMMs.R')
```

```{r LMM_table, message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
library(dplyr)
library(tidyr)
library(ggplot2)
library(papaja)
lmm_table <- apa_print(m1num2)
table2 <- data.frame(lmm_table$table)

table2 <- table2[-1, ]
table2[ ,1] <- c("Chord", "Register", "Expertise", "Chord $\\times$ Register", "Chord $\\times$ Expertise", "Register $\\times$ Expertise", "Chord $\\times$ Register $\\times$ Expertise")

apa_table(table2, caption = 'Linear Mixed Model analysis results for the consonance ratings for three Factors.',
row.names = F, escape = F
)

```

### Regression with the means

```{r regression, message=FALSE, warning=FALSE,echo=FALSE,fig.width=9,fig.height=11, fig.cap='Cubic model fit to (A) mean consonance ratings and (B) means across the chords.'}
source('regression_with_means.R')
print(G)
```

### Regression with the acoustic variables

```{r regression_acoustic,warning=FALSE,messages=FALSE,echo=FALSE,results='asis'}
source('regression_acoustic.R')

papaja::apa_table(
  acoust_lm$table
  , caption = "A regression table with the two acoustic predictors."
)

```
